CITK - an architecture and examples of CUDA enabled ITK filters

### 2011-08-24 article/Article.tex
changed email to upper case

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
  Parkinson, Phil Ward{$^2$}, Wojtek Goscinski{$1$}, Mike Kuiper{$^3$}}
\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia.\\
{$^2$}P.ward@csiro.au, CSIRO Land and Water, Highett, Australia.\\
{$^3$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}

>>>>

% At minimum, give your name and an email address.  You can include a
% snail-mail address if you like.
\author{Richard Beare{$^1$}, Daniel Micevski, Chris Share\\Luke
  Parkinson, Phil Ward{$^2$}, Wojtek Goscinski{$1$}, Mike Kuiper{$^3$}}
\authoraddress{{$^1$}Richard.Beare@monash.edu, Monash University, Melbourne, Australia.\\
{$^2$}P.Ward@csiro.au, CSIRO Land and Water, Highett, Australia.\\
{$^3$}mike@vpac.org, Victorian Partnership for Advanced Computing, Melbourne, Australia.}
